Project Proposal Machine Learning

### 2012-09-17 ProjectProposal/Project.tex
Last changes.

\paragraph{Application}

@@

We will obtain our training data from the CoNLL-2003\cite{TjongKimSang:2003:ICS:1119176.1119195} dataset, which contains
data in English and German. Additionally, we may also use the CoNLL-2002 data for Dutch and Spanish.  Table~\ref{table:input} shows the size of the input data and Table~\ref{table:output} shows the types and amount of Named Entity annotations on the input data for German and English.

>>>>

\paragraph{Application:}

@@

We will obtain our training data from the CoNLL-2003 dataset \cite{TjongKimSang:2003:ICS:1119176.1119195}, which contains
data in English and German. Additionally, we may also use the CoNLL-2002 data for Dutch and Spanish.  Table~\ref{table:input} shows the size of the input data and Table~\ref{table:output} shows the types and counts of Named Entity annotations on the input data for German and English.
